Proof nets for first-order additive linear logic

### 2018-01-22 ALL1.tex
fixed url

\author[1]{Willem B.\ Heijltjes}
\author[2]{Dominic J.D.\ Hughes}
\author[3]{Lutz Stra\ss burger}
\affil[1]{University of Bath, United Kingdom\\
  \texttt{http://www.cs.bath.ac.uk/~wbh22/}} %%w.b.heijltjes@bath.ac.uk}}
\affil[2]{Logic Group, UC Berkeley, USA\\
  \texttt{http://boole.stanford.edu/~dominic/}} %%dominich@theory.stanford.edu}}
\affil[3]{Inria Saclay \&\ LIX/\'Ecole Polytechnique, Palaiseau, France\\
  \texttt{http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger/}} %%lutz.strassburger@inria.fr}}
\authorrunning{W.B.\ Heijltjes, D.J.D.\ Hughes, and L.\ Stra\ss burger}

>>>>

\author[1]{Willem B.\ Heijltjes}
\author[2]{Dominic J.D.\ Hughes}
\author[3]{Lutz Stra\ss burger}
\affil[1]{University of Bath, United Kingdom\\
  \url{http://www.cs.bath.ac.uk/~wbh22/}} %%\texttt{w.b.heijltjes@bath.ac.uk}}
\affil[2]{Logic Group, UC Berkeley, USA\\
  \url{http://boole.stanford.edu/~dominic/}} %%\texttt{dominich@theory.stanford.edu}}
\affil[3]{Inria Saclay \&\ LIX/\'Ecole Polytechnique, Palaiseau, France\\
  \url{http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger/}} %%\texttt{lutz.strassburger@inria.fr}}
\authorrunning{W.B.\ Heijltjes, D.J.D.\ Hughes, and L.\ Stra\ss burger}
